---
title: "DataWrangling"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Load in Packages / Data
```{r}
library(tidyverse)
library(here)
library(lubridate)

seaotter_data <- read.csv(here("Data/GLBA_SEOT_forage_bouts_1993-2019(1).csv"))
```

# Create Year and Month Columns / Filter for Variables of Interest / Rid NAs

```{r}
seaotter_data$bout_date <- ymd(seaotter_data$bout_date)

seaotter_data <- seaotter_data %>%
  mutate(year = year(bout_date)) %>%
  mutate(month = month(bout_date)) %>%
  filter(site_name != "") %>%
  filter(preysize_cd != "") %>%
  select("bout_date", "year", "month", "sex_cd", "site_name", "dive_time", "success_cd", "preytype_cd", "prey_qty", "preysize_cd")
  
seaotter_data <- na.omit(seaotter_data)
```


# Do successful foraging attempts of sea otters within the Glacier Bay National Park vary geographically (different sites)?
```{r}
# Site name, Success = Yes, Count

seaotter_success <- seaotter_data %>%
  filter(success_cd == "y") %>%
  group_by (site_name) %>%
  count(success_cd) %>%
  rename(count = "n")
  
# definitely do facet_wrap(~site_name) for graphing

```
histogram of success per site


# Has prey type/quantity of sea otters within Glacier Bay National Park changed over time?
```{r}
seaotter_preytype <- 



```
scatterplot of grouped food types over time


# Does the proportion of successful foraging attempts of sea others within Glacier Bay National Park vary with gender or dive time?

```{r}



```



